Exploring Rural Shrink Smart Through Guided Discovery Dashboards

### 2022-04-08 Abstract Files/SCCAbstract_SDSS2022-knitr.tex
Cleaning up the repo

\begin{figure}[ht!]
\centering
\includegraphics[width=60mm]{SCC_Dashboard_pcp2.png}
\caption{Rural Smart EDA Dashboard Design}
\end{figure}

\section{User Testing}
\svp{In this paper, we present the results from testing this application with users, and examine the implications for the feedback we received on our application design and on the more general design of dashboards for statistical novices. We examine which aspects of dashboard design ``common knowledge" hold up in practice, and assess why these principles may not hold in our use-case.}

\svp{Complex visualizations are difficult to assess in vivo: it is fairly easy to design an experiment to test a single graphic, but much harder to test the interactive dashboards which consist of systems of displays and user interactions. As a result, it is important to continuously assess which ``common knowledge" design principles stemming from more controlled experiments hold up in real-world situations. }

>>>>

\begin{figure}[ht!]
\centering
\includegraphics[width=55mm]{SCC_Dashboard_pcp2.png}
\caption{Rural Smart EDA Dashboard Design}
\end{figure}

\section{User Testing}
In this paper, we present the results from testing this application with users, and examine the implications for the feedback we received on our application design and on the more general design of dashboards for statistical novices. We examine which aspects of dashboard design ``common knowledge'' hold up in practice, and assess why these principles may not hold in our use-case.

Complex visualizations are difficult to assess in vivo: it is fairly easy to design an experiment to test a single graphic, but much harder to test the interactive dashboards which consist of systems of displays and user interactions. As a result, it is important to continuously assess which ``common knowledge'' design principles stemming from more controlled experiments hold up in real-world situations.
